Efficient Feasibility Checking Algorithm of Photovoltaic Array Reconfiguration

### 2019-12-08 Journal-Photovoltaic/manuscript.tex
Finish section 1

% The main challenge in the reconfiguration of PV arrays concerns a large number of possibilities that must be evaluated to find the best solution.
This paper proposes an optimization algorithm to check possibilities of configurations for reconfiguring PV arrays, which uses an approach that 
\section{Conclusion}
The conclusion goes here.

>>>>

% The main challenge in the reconfiguration of PV arrays concerns a large number of possibilities that must be evaluated to find the best solution.
This paper proposes an optimization algorithm to check possibilities of configurations for reconfiguring PV arrays, which uses an approach that limit and sort possible combinations by the index of ``Loss-rate''.
Proposed feasibility checking algorithm can rapidly check feasibility that a given configuration candidate can be actually formed by given PV panels.
The experimental results demonstrate the effectiveness of the proposed method where it can identify the feasibility of configurations with a very small false negative rate of less than 1\%.

\section{Photovoltaic Array}

\section{Conclusion}
The conclusion goes here.
